---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo=FALSE}
library(SunsetTSA)
```

The SunsetTSA package contains a `sunrise_sunset()` function to get sunrise and sunset times at any U.S. airport by airport code. Data come from a U.S. Transportation Security Administration API (no key needed).

The package also includes several functions to look up three-letter codes for U.S. airports.

The package is currently not on CRAN so it needs to be installed from GitHub. To install it, you can use any number of packages and functions, including `remotes::install_github("smach/SunsetTSA")` or `githubinstall::githubinstall("SunsetTSA")` (`githubinstall()` attempts to find a package on GitHub even if you don't know the repo owner's account, and then asks you if you want to install the version it finds.)

###Get sunrise and sunset times

Run `sunrise_sunset("3-letter airport code")` to get a list with Sunrise, Sunset, Date, and Location (which is the airport code you entered). If you don't specify a date, it defaults to today. For example:

```{r}
sunrise_sunset("BOS")
```

To get results for another day, enter a date in `"yyyy-mm-dd"` format, such as this for Anchorage, Alaska's main airport on the 2020 summer solstice:

```{r}
sunrise_sunset("ANC", "2020-06-20")
```

###Get 3-letter airport codes

SunsetTSA also has several functions for looking up 3-letter airport codes. It will return a data frame with any matches including columns for Code, City, State, and Airport.

Data come from the U.S. Bureau of Transportation Statistics; I downloaded a CSV file from [https://www.transtats.bts.gov/Download_Lookup.asp?Lookup=L_AIRPORT](https://www.transtats.bts.gov/Download_Lookup.asp?Lookup=L_AIRPORT).

####By city name

The `airport_codes_by_city()` function has one required argument, city name, and an optional state name, such as:

```{r}
airport_codes_by_city("Providence")
airport_codes_by_city("Greenville", "SC")
```

####All codes in a state

The `all_airport_codes_by_state()` function will return all available codes in a state, with the two-letter postal abbreviation as the argument:

```{r}
all_airport_codes_by_state("RI")
```

####Code by airport name

You can also try looking up the code by airport name or partial airport name with `airport_codes_by_name()`. However, you'll need part of the _same name that the Bureau of Transportation uses._ So, while you may refer to one of New York City's airport as "JFK", you'd need to know that it's "John F. Kennedy International" to the BTS. "Kennedy" would also work:

```{r}
airport_codes_by_name("Kennedy")
```

